The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-30 paper/ms.tex
number of quarters

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $V=8$ in the \kepler field. This sample is biased towards red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and solar-like oscillations in \textcolor{red}{$N$}~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<8$ which were unobserved for more than $10$ quarters \textcolor{red}{Tim: what was your cutoff in quarters for `underobserved' stars?}, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.

>>>>

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample is biased towards red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and solar-like oscillations in \textcolor{red}{$N$}~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.
